Adopting agile in the large: motivations, success factors and challenges

### 2014-04-13 journal/article.tex
Organization size; multiple case studies numbered as separate organizations

In several cases the transformation of a single organization was described in
more than one primary study. Even if the transformation of a single organization
was described in many studies all sources that passed the inclusion criterial
were included. The reason for this was that we wanted to gain as much insight
from each organization as possible. As a result 40 unique organizations were
identified in the primary studies.

@@

The results of this study include findings from 52 primary studies presenting
how 40 different large organizations introduce agile software development. Most
of the included studies were experience reports (45 studies), and in many cases
it was evident that the author had been personally involved in the transformation.
Only 6 of the included studies had a research method explicitly stated. One of
the studies was an interview article. The publication forums of the primary
studies were distributed so that 57 sources were conference proceedings, 4
sources were journal articles, and one source was a technical report.

@@

Organization size varied 50 -- 15000. Median.

>>>>

In several cases there were more than one primary study presenting the
transformation of the same organization. Even if the transformation of a single
organization was described in many studies all sources that passed the inclusion
criterial were included. Studies presenting the same organization were treated
as one unit so that we could gain as much insight from each organization as
possible. There were also a few papers that presented multiple case studies, and
in those cases we treated each studied organization individually. As a result 42
unique organizations were identified in the primary studies.

@@

The results of this study include findings from 52 primary studies presenting
how 42 different large software organizations introduce agile methods. Most of
the included studies were experience reports (45 studies), and in many cases it
was evident that the author had been personally involved in the transformation.
Only 6 of the included studies had a research method explicitly stated. One of
the studies was an interview article. The publication forums of the primary
studies were distributed so that 57 sources were conference proceedings, 4
sources were journal articles, and one source was a technical report.

The size of the organizations varied from the minimum included size of 50 to
18,000 people. The median size was 300 people. In 7 studies the size was
presented in terms of teams, ranging from the minimum of 6 teams to 150 teams.
The median was 10 teams. In 8 studies there was no direct indication on size
but the issues discussed revealed that the organization was of large size
accoding to our definition.

@@
